Detailed Chemical Abundances with \tc

### 2015-08-28 article/ms.tex
First draft of abstract

\begin{abstract}
% large surveys spectroscopically planned.
% poses computing challenge.
% commonalityies between them: all R ~ 20,000, trying to get abundances from
% weak lines, which are linearly responsive (therefore best indicators) of
% abundance.
% TC provides a purely data-driven approach to stellar parameter (label)
% determination.
% fast, accurate, limited by systematics (which are low), meaning it works well
% in low S/N. Perfect for survey work.
% Simply extending dimensionality of the Cannon to include individual abundances
% can create enormous difficulties, both in potentially overfitting and curse of DIm.
% These extensions also imply a purely data-driven approach to abundances.
% Here we include radiative transfer physics to explain why a polynomial extension
% works so well, and provide a simple model to relate individual chemical
% abundance (and teh stellar parameter labels) to a flux value.
% We provide a direct link between model atmosphere physics and data-driven
% approaches, allowing the data to inform models.
% We demonstrate that individual abundances can be determined with a precision of
% X using our models. These determinations are fast: we estimate all 15 APOGEE 
% elemental abundances (and stellar parameters) for 60,000 stars on a modern
% laptop in 5 minutes.

\end{abstract}

>>>>

\begin{abstract}
More than 15 million spectra are expected to be acquired by stellar surveys in
the coming decade. The detailed chemical abundance analysis of these data poses
a significant computational challenge. \tc provides a purely data-driven
approach to stellar parameter (label) determination. Cross-validation tests
demonstrate that the precision achievable is comparable to existing methods that
rely on model atmospheres and spectral synthesis, but \tc is $\sim300,000\times$ faster, making it perfectly apt for surveys. Simply extending the label vector
dimensionality of \tc to include individual abundances can create enormous
model difficulties, severely limiting the interpretability of the results. Here
we describe an alternative approach to including individual element abundances
in \tc. Using modest simplifications of the physics of spectral line formation,
we demonstrate precisely \textit{why} an approach like \tc works so effectively,
and provide a physically-motivated model that describes flux values, given the
stellar parameters. The inclusion of individual chemical abundances does not
impact on model flexibility, allowing for simultaneous training on detailed
chemical abundances, as well as arbitrary labels where the impact on the spectra
is unknown or poorly understood (e.g., mass, age). Crucially, we provide a link
between data-driven models and parallel works on model atmospheres and spectral
line formation, allowing for data to inform models. We demonstrate that
detailed chemical abundances can be measured with a precision of 0.0X-0.0Y~dex
in Z APOGEE spectra on a modern CPU in just one minute.
\end{abstract}
